Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-10-19 paper/paper.tex
Make UAV and robot animation

\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage}
% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
% Jr}.\authorrefmark{3},
% \IEEEmembership{Member, IEEE}}
% \address[1]{National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA}
% \tfootnote{This paragraph of the first footnote will contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.''}

@@

\section{PRELIMINARIES OF S\&R URTS}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation. This problem is refered as a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}. Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a destinition $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{4,1},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{4,1}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

@@

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary. (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot). In this case, a unified planner will become overly complex and impracticable. For this reason, we divide path planning into three subprocesses, i.e., Path Planning, Behavior Layer and Local Motion Planning. Then, the global planner, Path Planning block, will regard an agent as a point without kinodynamic constraints. The local planners, Local Motion Planning block, will consider the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

@@

\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have a perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtained.
\end{assumption}
\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
    UAVs do not consider obstacle collisions because there are few obstacles in the air. Hence, the path of UAVs can be directly assigned rather than found by planner. Robots do not consider obstacle collisions in the direction perpendicular to the ground. 
\end{assumption}

From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that is made by human or Task Allocation. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to the next block, Behavior Layer.

@@

\section{simulation results}
In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy. First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig. \ref{fig:SR_area}. To simplify the description, we will focus on the UAV and robot in $1$st team. Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$. At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupy map and find targets. The search task is assumed to be obtained by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$. Suppose a target is found after a while as shown in Fig. \ref{fig:S_task}, at this point, we have a rescue task $T_6$. The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{1,2}$ and $\alpha_{1,3}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,2},T_2),(\alpha_{1,3},T_3) \})\cup\{ \alpha_{1,2},T_6),(\alpha_{1,3},T_6) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining. The search tasks $T_j,j=1,2,...,5$ are to reach a destinition $q_{goal}$ as shown in figure. For robots, $q_{goal}$ will be passed to path planning algorithm to find a collision path. For UAV, the path is directly assigned due to the no-collision assumption as shown in figure.}%
    \label{fig:S_task}
\end{figure}

To explain the path planning block and behavior layer block, we choose the pair $(\alpha_{1,2},T_6)$ as an example, i.e., the robot $\alpha_{1,2}$ performing the task $T_6$. From $T_6$, we have the goal configuration $q_{goal}$. With the current configuration $q_{start}$ and configuration space obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig. \ref{fig:R_task}. The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking},n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing},n\in\mathbb{Z}\cap[6,15]$, $\beta_n=\mathit{running},n\in\mathbb{Z}\cap[16,27]$. We choose the first walking behavior to illustrate the local motion planning block of robots.

For the the UAV $\alpha_{1,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}. The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The path planning tasks.}%
    \label{fig:R_task}
\end{figure}

>>>>

\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage}
% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
% Jr}.\authorrefmark{3},
% \IEEEmembership{Member, IEEE}}
% \address[1]{National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA}
% \tfootnote{This paragraph of the first footnote will contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.''}

@@

\section{PRELIMINARIES OF S\&R URTS}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{j,i}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation. This problem is refered as a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}. Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a destinition $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

@@

\begin{remark}
    To avoid agents colliding with each other, the concept of multi-agent path planning is proposed \cite{yu2013multi}. However, URTS operates in a large environment so the probability of collision is small and the agents have the ability to communicate. Therefore, when the paths collide, the mechanism of waiting for the other side to pass can be used to avoid the collision problem.
\end{remark}

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary. (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot). In this case, a unified planner will become overly complex and impracticable. For this reason, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning. Then, the global planner, path planning block, will regard an agent as a point without kinodynamic constraints. The local planners, local motion planning block, will consider the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

@@

\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have a perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtained.
\end{assumption}
\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
    UAVs do not consider obstacle collision, so the path of UAVs can be directly assigned rather than found by planner. Robots do not consider obstacle collision in the direction perpendicular to the ground. 
\end{assumption}

From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that is made by human or task allocation block. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to the next block, Behavior Layer.

@@

\section{simulation results}
In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy. First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig. \ref{fig:SR_area}. To simplify the description, we will focus on the UAV and robot in $1$st team. Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$. At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupy map and find targets. The search task is assumed to be obtained by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$. Suppose a target is found after a while as shown in Fig. \ref{fig:S_task}, at this point, we have a rescue task $T_6$. The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{1,5}$ and $\alpha_{2,2}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,5},T_2),(\alpha_{2,2},T_3) \})\cup\{ (\alpha_{1,5},T_6),(\alpha_{2,2},T_6) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining. The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinitions $q_{goal}$ (black dots in figure). For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths. For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption.}
    \label{fig:S_task}
\end{figure}

To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{1,5},T_6)$ and $(\alpha_{1,1}, T_1)$ as example. For the robot $\alpha_{1,5}$, we have the goal configuration $q_{goal}$ from the task $T_6$. With the current configuration $q_{start}$ and configuration space $\mathcal{C}$ obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig. \ref{fig:R_task}. The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking}$ for $n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing}$ for $n\in\mathbb{Z}\cap[6,15]$ and $\beta_n=\mathit{running}$ for $n\in\mathbb{Z}\cap[16,27]$. We choose the walking behavior to illustrate the local motion planning block of robots.

For the UAV $\alpha_{1,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}. The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The path planning tasks.}%
    \label{fig:R_task}
\end{figure}
